\documentclass[11pt,letterpaper,oneside]{ucletter}

%if you do not have this package installed, it will be okay.
%\usepackage{universityos}

\usepackage{xspace}
\usepackage{listings}

\name{C. Titus Brown (corresponding author)}
\address{Associate Professor \\
Department of Population Health and Reproduction \\
University of California, Davis \\
Davis, CA 95616} 

\signature{C. Titus Brown}

%\textheight 645pt
%\textheight 8.4in
%\textwidth 6.4in
%\oddsidemargin 0cm

\begin{document}

\begin{letter}
{F1000 Research Editorial Board} 

\opening{Dear Editors,}


We are submitting our software article entitled ``Large Scale Sequence Comparisons with \lstinline{sourmash}" for consideration for publication in F1000 Research. 

Bioinformatic analyses rely on sequence comparison for applications ranging from functional annotation and variant analysis to taxonomic annotation. With continuing increases in sequencing power, there has been great need for methods and tools that quickly and efficiently conduct sequence similarity searches on a massive scale. Here we present version 2.0 of \lstinline{sourmash}, a Python library for building and utilizing MinHash sketches of DNA, RNA, and protein data. \lstinline{sourmash} incorporates and extends standard MinHash techniques for sequencing data, with a particular focus towards enabling efficient containment queries using large databases and in a streaming-compatible manner. In addition, \lstinline{sourmash} provides a user-friendly, extensible platform for MinHash signature generation and manipulation.

This manuscript describes the \lstinline{sourmash} software package and provides a number of informative use cases to introduce the reader to this software. It has not been previously published, nor has it been submitted simultaneously for publication elsewhere. All authors consent to submission of this manuscript, and have no conflicts of interest to disclose.


Thank you for your consideration.

\closing{Sincerely,}

\end{letter}

\end{document}



